Evaluating infectious disease forecasts \\ with allocation scoring rules

### 2024-01-29 alloscore_manuscript/alloscore-application-shorter.Rnw
adding comments addressed through section 2.

Infectious disease forecasting models have emerged as important tools in public health. Predictions of disease dynamics have been used to inform decision making about a wide variety of measures to reduce disease spread and/or mitigate the severity of disease outcomes. For example, estimates of expected onset of flu season have been used to aid national vaccination strategies \citep{igboh2023timing}, and forecasts of Ebola and diptheria dynamics have been used to allocate resources \citep{meltzer2014estimating, rainisch2015regional,camacho2015-ebola-bed,finger_real-time_2019}. \cite{bertsimas2021predictionsCOVID} developed tools to guide decision making from infectious disease forecasts, which have been used to inform allocation of limited medical supplies such as ventilators, ICU capacity planning, and vaccine distribution strategy. Models developed by \cite{fox_real-time_2022} have been used to inform resource and care site planning, as well as community guidelines for masking, traveling, dining and shopping (University of Texas, 2022)\nocite{utnews2022}.
%In April of 2022, the Centers for Disease Control and Prevention (CDC) announced the launch of the Center for Forecasting and Outbreak Analytics (CFA) to translate disease forecasts into decision making (CDC, 2022)\nocite{cdc2022cfa}, indicating that this has been identified as an important direction at the highest levels of government public health response.
%The value of infectious disease forecasts has typically been measured by how closely they predict disease outcomes such as cases, hospitalizations or deaths using, for example, root mean square error (RMSE) \citep{papastefanopoulos2020covid} or weighted interval score (WIS) \citep{bracher2021evaluating}.  However, recently authors have been calling for evaluating forecasts through their impact on policy \citep{marshall2023predictions, bilinski_adaptive_2023}.

In decision making settings where it is possible to quantify the utility or loss associated with a particular action, standard tools of decision theory provide a procedure for developing forecast scoring rules that measure the value of forecasts through the quality of the decisions that they lead to. We give an overview of these procedures in Section \ref{sec:methods.detailed.decisiontheory}.
There is a large history of literature applying these ideas to obtain measures of the value of forecasts that are tied to a decision making context, primarily in fields such as economics and finance, supply chain management, and meteorology. We review this work only briefly here, and we refer the reader to \cite{yardley2021utility_cost_forecasts} for a general overview, and to \cite{pesaran2002decision_based_eval} and \cite{murphy1993whatisagoodforecast} for discussions focused on applications to economics and meteorology, respectively. In finance, the value of forecasts can often be measured by the profits generated by trading decisions informed by the forecasts, perhaps adjusted for risk levels \cite[e.g.,][]{leitch1991economicForecastEval, cenesizoglu2012returnPredictionEconValue}. In applications to supply chain management and meteorology, the value of forecasts has typically been operationalized by considering the costs associated with decisions regarding the amount of inventory to hold or the level of protection against the impacts of extreme weather events to enact \cite[e.g.,][]{catt2007assessingcostofforecasterror, petropoulos2019inventoryperformanceforecasting, palmer2002economic, pappenberger2015monetarybenefitfloodwarnings}. For example, in supply chain management these decisions may incur costs related to holding inventory, labor, or providing poor service, while in meteorology we may need to balance the costs of implementing protective measures with the costs of potentially preventable weather damages. In this framework, a forecast has value if it leads to decisions with low total costs. In all of these fields, analyses have consistently found that common measures of statistical forecast accuracy do not necessarily correspond directly to measures of the value of forecasts as an input to decision making \cite[e.g.,][]{leitch1991economicForecastEval, murphy1993whatisagoodforecast, cenesizoglu2012returnPredictionEconValue}.

However, we are aware of only a limited body of work that explicitly attempts to measure the value of infectious disease forecasts through their impact on policy, and much of this discussion has proceeded informally. For example, \cite{ioannidis2022forecastingCOVIDfailed} discuss the possible negative consequences of inaccurate forecasts of infectious disease, but do not attempt to quantify the utility or loss incurred as a result of those forecasts. \cite{bilinski_adaptive_2023} explore ways in which policymaker preferences could inform risk thresholds for predictive models using a framework for measuring the costs and losses associated with taking an action that is similar to methods that have been used in meteorology and elsewhere. \cite{marshall2023predictions} develop a forecast scoring rule that is informally motivated by utility considerations, but the score is not derived from a decision-theoretic set up. Separately, there is a thread of literature that quantifies the link between infectious disease modeling and policy making outside of a forecasting context. As an example, \cite{Probert2016decisionMakingFootMouth} develop measures of the cost of actions designed to control a hypothetical outbreak of foot-and-mouth disease and use this framework to explore policy recommendations from a variety of simulation-based projection models.

In practice, probabilistic infectious disease forecasts have most often been made for observations that emerge from public health surveillance systems and have typically been evaluated with standard, ``off-the-shelf'' scoring rules.
For example, seasonal influenza forecasts in the US and dengue forecasts for Peru and Puerto Rico targeted public health surveillance measures of incidence over time and space, and used log-score and mean absolute errors to evaluate forecast skill \citep{mcgowan_collaborative_2019,reich_collaborative_2019,johansson_open_2019}.
Pandemic COVID-19 forecasts of observed cases, hospitalizations and/or deaths in the US and Europe, as reported by municipal, state, or federal surveillance systems, were evaluated using the weighted interval score (WIS, which is an approximation of the continuous ranked probability score, or CRPS), and prediction interval coverage \citep{cramer_evaluation_2022,fox_real-time_2022,sherratt2023predictive}.
Similarly, CRPS was also used to assess probabilistic forecasts of dengue incidence at the district level in Vietnam \citep{colon-gonzalez_probabilistic_2021}.
While some of these scores can be interpreted through the lens of decision theory, and all of the application-specific papers cited above had authors from public health agencies, none of them make explicit connections between forecast evaluation and how a forecast was used in practice.

@@

We can formalize the preceding discussion with the following three-step procedure for developing scoring rules for probabilistic forecasts:
\begin{enumerate}
\item Specify a \emph{loss function} $s(x, y)$ that measures the loss associated with taking action $x$ when outcome $y$ eventually occurs.
\item Given a probabilistic forecast $F$, determine the \emph{Bayes act} $x^F$ that minimizes the expected loss under the distribution $F$.
\item The \emph{scoring rule} for $F$ calculates the score as the loss incurred when the Bayes act was used: $S(F, y) = s(x^F, y)$.
\end{enumerate}
This is a general procedure that may be applied in settings where it is possible to specify a quantitative loss function. We call a scoring rule obtained from this procedure a \emph{Bayes scoring rule} and in section \ref{sec:proper} of the
supplement we show that Bayes scoring rules are proper by construction.

>>>>

Infectious disease forecasting models have emerged as important tools in public health outbreak response. Predictions of disease dynamics have been used to inform decision making about a wide variety of measures to reduce disease spread and/or mitigate the severity of disease outcomes. For example, estimates of expected onset of flu season have been used to aid national vaccination strategies \citep{igboh2023timing}, and forecasts of Ebola and diptheria dynamics have been used to allocate resources \citep{meltzer2014estimating, rainisch2015regional,camacho2015-ebola-bed,finger_real-time_2019}. \cite{bertsimas2021predictionsCOVID} developed tools to guide decision making from infectious disease forecasts, which have been used to inform allocation of limited resources such as ventilators, ICU capacity, and vaccine supply. Models developed by \cite{fox_real-time_2022} have been used to inform resource and care site planning, as well as community guidelines for masking, traveling, dining and shopping (University of Texas, 2022)\nocite{utnews2022}.
%In April of 2022, the Centers for Disease Control and Prevention (CDC) announced the launch of the Center for Forecasting and Outbreak Analytics (CFA) to translate disease forecasts into decision making (CDC, 2022)\nocite{cdc2022cfa}, indicating that this has been identified as an important direction at the highest levels of government public health response.

In the wake of the COVID-19 pandemic, researchers have been calling for evaluating forecasts through their impact on policy \citep{marshall2023predictions, bilinski_adaptive_2023}.
The value of infectious disease forecasts has typically been measured by how closely they predict disease outcomes such as cases, hospitalizations or deaths using, for example, root mean square error (RMSE) \citep{papastefanopoulos2020covid}, log-score \citep{mcgowan_collaborative_2019}, or weighted interval score (WIS) \citep{bracher2021evaluating}.
However, as we show in this paper, these metrics only evaluate one specific dimension of accuracy, and often do not have a clear correspondence to features that would make a forecast valuable in the context of a specific decision.
While these ideas have received little attention in the context of infectious disease forecasting, the results are well known from other fields, such as economics and finance, supply chain management, and meteorology.

In decision making settings where it is possible to quantify the utility or loss associated with a particular action, standard tools of decision theory provide a procedure for developing forecast scoring rules that measure the value of forecasts through the quality of the decisions that they lead to (see details in Section \ref{sec:methods.detailed.decisiontheory}).
%There is a large history of literature applying these ideas to obtain measures of the value of forecasts that are tied to a decision making context, primarily in fields such as economics and finance, supply chain management, and meteorology.
We refer the reader to \cite{yardley2021utility_cost_forecasts} for a general overview, and to \cite{pesaran2002decision_based_eval} and \cite{murphy1993whatisagoodforecast} for discussions focused on applications to economics and meteorology, respectively.
%In finance, the value of forecasts can often be measured by the profits generated by trading decisions informed by the forecasts, perhaps adjusted for risk levels \cite[e.g.,][]{leitch1991economicForecastEval, cenesizoglu2012returnPredictionEconValue}. In applications to supply chain management and meteorology, the value of forecasts has typically been operationalized by considering the costs associated with decisions regarding the amount of inventory to hold or the level of protection against the impacts of extreme weather events to enact \cite[e.g.,][]{catt2007assessingcostofforecasterror, petropoulos2019inventoryperformanceforecasting, palmer2002economic, pappenberger2015monetarybenefitfloodwarnings}.
In this framework, a forecast has value if it leads to decisions with low total costs.
As one example,
% in supply chain management these decisions may incur costs related to holding inventory, labor, or providing poor service, while
in meteorology, policy makers need to balance the costs of implementing protective measures with the costs of potentially preventable weather damages \citep{palmer2002economic, pappenberger2015monetarybenefitfloodwarnings}.
Across many fields, analyses have consistently found that common measures of forecast accuracy do not necessarily correspond directly to measures of the value of forecasts as an input to decision making \cite[e.g.,][]{leitch1991economicForecastEval, murphy1993whatisagoodforecast, cenesizoglu2012returnPredictionEconValue}.

We are aware of only a limited body of work that explicitly attempts to measure the value of infectious disease forecasts through their impact on policy. For example, \cite{ioannidis2022forecastingCOVIDfailed} discuss the possible negative consequences of inaccurate forecasts of infectious disease, but do not attempt to quantify the utility or loss incurred as a result of those forecasts. \cite{bilinski_adaptive_2023} explore ways in which policymaker preferences could inform risk thresholds for predictive models using a framework for measuring the costs and losses associated with taking an action that is similar to methods that have been used in meteorology and elsewhere. \cite{marshall2023predictions} develop a forecast scoring rule that is informally motivated by utility considerations, but the score is not derived from a decision-theoretic set up. Separately, there is a thread of literature that quantifies the link between infectious disease modeling and policy making outside of a forecasting context. As an example, \cite{Probert2016decisionMakingFootMouth} develop measures of the cost of actions designed to control a hypothetical outbreak of foot-and-mouth disease and use this framework to explore policy recommendations from a variety of simulation-based projection models.

In practice, probabilistic infectious disease forecasts have most often been made for observations that emerge from public health surveillance systems and have typically been evaluated with common scoring rules that have implementations available in existing software packages.
For example, seasonal influenza forecasts in the US and dengue forecasts for Peru and Puerto Rico targeted public health surveillance measures of incidence over time and space, and used log-score and mean absolute errors to evaluate forecast skill \citep{mcgowan_collaborative_2019,reich_collaborative_2019,johansson_open_2019}.
Pandemic COVID-19 forecasts of observed cases, hospitalizations and/or deaths in the US and Europe, as reported by municipal, state, or federal surveillance systems, were evaluated using the weighted interval score (WIS, which is an approximation of the continuous ranked probability score, or CRPS), and prediction interval coverage \citep{cramer_evaluation_2022,fox_real-time_2022,sherratt2023predictive}.
Similarly, CRPS was also used to assess probabilistic forecasts of dengue incidence at the district level in Vietnam \citep{colon-gonzalez_probabilistic_2021}.
While some of these scores can be interpreted through the lens of decision theory, and all of the application-specific papers cited above have benefited from direct collaboration with public health agencies, none of them make explicit connections between forecast evaluation and how a forecast was used in practice.

@@

We can formalize the preceding discussion with the following three-step procedure for developing scoring rules for probabilistic forecasts:
\begin{enumerate}
\item Specify a \emph{loss function} $s(x, y)$ that measures the loss associated with taking action $x$ when outcome $y$ eventually occurs.
\item Given a probabilistic forecast $F$, determine the \emph{Bayes act} $x^F$ that minimizes the expected loss under the distribution $F$.
\item The \emph{scoring rule} for $F$ calculates the score as the loss incurred when the Bayes act was used: $S(F, y) = s(x^F, y)$.
\end{enumerate}
This is a general procedure that may be applied in settings where it is possible to specify a quantitative loss function. We call a scoring rule obtained from this procedure a \emph{Bayes scoring rule} and in section \ref{sec:proper} of the
supplement we demonstrate that Bayes scoring rules are proper by construction (a result also shown by \cite{dawid2007geometry,gneiting2007strictly}).

### 2024-01-29 alloscore_manuscript/alloscore-application-shorter.tex
adding comments addressed through section 2.

\title{Evaluating infectious disease forecasts with allocation scoring rules}
\author{Aaron Gerding, Nicholas G. Reich, Benjamin Rogers, Evan L. Ray}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

Infectious disease forecasting models have emerged as important tools in public health. Predictions of disease dynamics have been used to inform decision making about a wide variety of measures to reduce disease spread and/or mitigate the severity of disease outcomes. For example, estimates of expected onset of flu season have been used to aid national vaccination strategies \citep{igboh2023timing}, and forecasts of Ebola dynamics have been used to allocate surveillance resources \citep{meltzer2014estimating, rainisch2015regional}. \cite{bertsimas2021predictionsCOVID} developed tools to guide decision making from infectious disease forecasts, which have been used to inform allocation of limited medical supplies such as ventilators, ICU capacity planning, and vaccine distribution strategy. Models developed by \cite{fox_real-time_2022} have been used to inform resource and care site planning, as well as community guidelines for masking, traveling, dining and shopping (University of Texas, 2022)\nocite{utnews2022}.
%In April of 2022, the Centers for Disease Control and Prevention (CDC) announced the launch of the Center for Forecasting and Outbreak Analytics (CFA) to translate disease forecasts into decision making (CDC, 2022)\nocite{cdc2022cfa}, indicating that this has been identified as an important direction at the highest levels of government public health response.
%The value of infectious disease forecasts has typically been measured by how closely they predict disease outcomes such as cases, hospitalizations or deaths using, for example, root mean square error (RMSE) \citep{papastefanopoulos2020covid} or weighted interval score (WIS) \citep{bracher2021evaluating}.  However, recently authors have been calling for evaluating forecasts through their impact on policy \citep{marshall2023predictions, bilinski_adaptive_2023}.

In decision making settings where it is possible to quantify the utility or loss associated with a particular action, standard tools of decision theory provide a procedure for developing forecast scoring rules that measure the value of forecasts through the quality of the decisions that they lead to. We give an overview of these procedures in Section \ref{sec:methods.detailed.decisiontheory}.
There is a large history of literature applying these ideas to obtain measures of the value of forecasts that are tied to a decision making context, primarily in fields such as economics and finance, supply chain management, and meteorology. We review this work only briefly here, and we refer the reader to \cite{yardley2021utility_cost_forecasts} for a general overview, and to \cite{pesaran2002decision_based_eval} and \cite{murphy1993whatisagoodforecast} for discussions focused on applications to economics and meteorology, respectively. In finance, the value of forecasts can often be measured by the profits generated by trading decisions informed by the forecasts, perhaps adjusted for risk levels \cite[e.g.,][]{leitch1991economicForecastEval, cenesizoglu2012returnPredictionEconValue}. In applications to supply chain management and meteorology, the value of forecasts has typically been operationalized by considering the costs associated with decisions regarding the amount of inventory to hold or the level of protection against the impacts of extreme weather events to enact \cite[e.g.,][]{catt2007assessingcostofforecasterror, petropoulos2019inventoryperformanceforecasting, palmer2002economic, pappenberger2015monetarybenefitfloodwarnings}. For example, in supply chain management these decisions may incur costs related to holding inventory, labor, or providing poor service, while in meteorology we may need to balance the costs of implementing protective measures with the costs of potentially preventable weather damages. In this framework, a forecast has value if it leads to decisions with low total costs. In all of these fields, analyses have consistently found that common measures of statistical forecast accuracy do not necessarily correspond directly to measures of the value of forecasts as an input to decision making \cite[e.g.,][]{leitch1991economicForecastEval, murphy1993whatisagoodforecast, cenesizoglu2012returnPredictionEconValue}.

However, we are aware of only a limited body of work that explicitly attempts to measure the value of infectious disease forecasts through their impact on policy, and much of this discussion has proceeded informally. For example, \cite{ioannidis2022forecastingCOVIDfailed} discuss the possible negative consequences of inaccurate forecasts of infectious disease, but do not attempt to quantify the utility or loss incurred as a result of those forecasts. \cite{bilinski_adaptive_2023} explore ways in which policymaker preferences could inform risk thresholds for predictive models using a framework for measuring the costs and losses associated with taking an action that is similar to methods that have been used in meteorology and elsewhere. \cite{marshall2023predictions} develop a forecast scoring rule that is informally motivated by utility considerations, but the score is not derived from a decision-theoretic set up. Separately, there is a thread of literature that quantifies the link between infectious disease modeling and policy making outside of a forecasting context. As an example, \cite{Probert2016decisionMakingFootMouth} develop measures of the cost of actions designed to control a hypothetical outbreak of foot-and-mouth disease and use this framework to explore policy recommendations from a variety of simulation-based projection models.

In practice, probabilistic infectious disease forecasts have most often been made for observations that emerge from public health surveillance systems and have typically been evaluated with standard, ``off-the-shelf'' scoring rules.
For example, seasonal influenza forecasts in the US and dengue forecasts for Peru and Puerto Rico targeted public health surveillance measures of incidence over time and space, and used log-score and mean absolute errors to evaluate forecast skill \citep{mcgowan_collaborative_2019,reich_collaborative_2019,johansson_open_2019}.
Pandemic COVID-19 forecasts of observed cases, hospitalizations and/or deaths in the US and Europe, as reported by municipal, state, or federal surveillance systems, were evaluated using the weighted interval score (WIS, which is an approximation of the continuous ranked probability score, or CRPS), and prediction interval coverage \citep{cramer_evaluation_2022,fox_real-time_2022,sherratt2023predictive}.
Similarly, CRPS was also used to assess probabilistic forecasts of dengue incidence at the district level in Vietnam \citep{colon-gonzalez_probabilistic_2021}.
While some of these scores can be interpreted through the lens of decision theory, and all of the application-specific papers cited above had authors from public health agencies, none of them make explicit connections between forecast evaluation and how a forecast was used in practice.

@@

% latex table generated in R 4.3.1 by xtable 1.8-4 package
% Fri Dec 22 10:45:01 2023
\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
Model & AS & MWIS & IAS centered at 15k & IAS uniform \\ 
  \hline
CU-select & 669 & 133 & 774 & 326 \\ 
  COVIDhub-ensemble & 873 & 159 & 1067 & 438 \\ 
  USC-SI\_kJalpha & 995 & 91 & 1216 & 1097 \\ 
  JHUAPL-Gecko & 1034 & 164 & 1141 & 418 \\ 
  MUNI-ARIMA & 1084 & 169 & 1248 & 440 \\ 
  COVIDhub-trained\_ensemble & 1089 & 169 & 1271 & 823 \\ 
  COVIDhub-baseline & 1175 & 170 & 1317 & 535 \\ 
  JHUAPL-Bucky & 1358 & 102 & 1566 & 1214 \\ 
  JHUAPL-SLPHospEns & 1540 & 129 & 1604 & 1102 \\ 
  UVA-Ensemble & 2469 & 213 & 2635 & 2494 \\ 
   \hline
\end{tabular}
\caption{Comparison of allocation scores (AS), mean weighted interval scores (MWIS), and two varieties of Integrated Allocation Scores (IAS). All metrics are shown for 10 models that made forecasts of hospital admissions for 2022-01-03. Results are sorted by AS. For all metrics, lower scores indicate better accuracy.} 
\label{tab:multi-k-scores}
\end{table}

@@

\section*{Acknowledgements}
This work has been supported by the National Institutes of General Medical Sciences (R35GM119582) and the U.S. CDC(1U01IP001122). The content is solely the responsibility of the authors and does not necessarily represent the official views of NIGMS, the National Institutes of Health, or CDC.

>>>>

\title{Evaluating infectious disease forecasts \\ with allocation scoring rules}
\author{Aaron Gerding, Nicholas G. Reich, Benjamin Rogers, Evan L. Ray}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

Infectious disease forecasting models have emerged as important tools in public health outbreak response. Predictions of disease dynamics have been used to inform decision making about a wide variety of measures to reduce disease spread and/or mitigate the severity of disease outcomes. For example, estimates of expected onset of flu season have been used to aid national vaccination strategies \citep{igboh2023timing}, and forecasts of Ebola and diptheria dynamics have been used to allocate resources \citep{meltzer2014estimating, rainisch2015regional,camacho2015-ebola-bed,finger_real-time_2019}. \cite{bertsimas2021predictionsCOVID} developed tools to guide decision making from infectious disease forecasts, which have been used to inform allocation of limited resources such as ventilators, ICU capacity, and vaccine supply. Models developed by \cite{fox_real-time_2022} have been used to inform resource and care site planning, as well as community guidelines for masking, traveling, dining and shopping (University of Texas, 2022)\nocite{utnews2022}.
%In April of 2022, the Centers for Disease Control and Prevention (CDC) announced the launch of the Center for Forecasting and Outbreak Analytics (CFA) to translate disease forecasts into decision making (CDC, 2022)\nocite{cdc2022cfa}, indicating that this has been identified as an important direction at the highest levels of government public health response.

In the wake of the COVID-19 pandemic, researchers have been calling for evaluating forecasts through their impact on policy \citep{marshall2023predictions, bilinski_adaptive_2023}.
The value of infectious disease forecasts has typically been measured by how closely they predict disease outcomes such as cases, hospitalizations or deaths using, for example, root mean square error (RMSE) \citep{papastefanopoulos2020covid}, log-score \citep{mcgowan_collaborative_2019}, or weighted interval score (WIS) \citep{bracher2021evaluating}.
However, as we show in this paper, these metrics only evaluate one specific dimension of accuracy, and often do not have a clear correspondence to features that would make a forecast valuable in the context of a specific decision.
While these ideas have received little attention in the context of infectious disease forecasting, the results are well known from other fields, such as economics and finance, supply chain management, and meteorology.

In decision making settings where it is possible to quantify the utility or loss associated with a particular action, standard tools of decision theory provide a procedure for developing forecast scoring rules that measure the value of forecasts through the quality of the decisions that they lead to (see details in Section \ref{sec:methods.detailed.decisiontheory}).
%There is a large history of literature applying these ideas to obtain measures of the value of forecasts that are tied to a decision making context, primarily in fields such as economics and finance, supply chain management, and meteorology.
We refer the reader to \cite{yardley2021utility_cost_forecasts} for a general overview, and to \cite{pesaran2002decision_based_eval} and \cite{murphy1993whatisagoodforecast} for discussions focused on applications to economics and meteorology, respectively.
%In finance, the value of forecasts can often be measured by the profits generated by trading decisions informed by the forecasts, perhaps adjusted for risk levels \cite[e.g.,][]{leitch1991economicForecastEval, cenesizoglu2012returnPredictionEconValue}. In applications to supply chain management and meteorology, the value of forecasts has typically been operationalized by considering the costs associated with decisions regarding the amount of inventory to hold or the level of protection against the impacts of extreme weather events to enact \cite[e.g.,][]{catt2007assessingcostofforecasterror, petropoulos2019inventoryperformanceforecasting, palmer2002economic, pappenberger2015monetarybenefitfloodwarnings}.
In this framework, a forecast has value if it leads to decisions with low total costs.
As one example,
% in supply chain management these decisions may incur costs related to holding inventory, labor, or providing poor service, while
in meteorology, policy makers need to balance the costs of implementing protective measures with the costs of potentially preventable weather damages \citep{palmer2002economic, pappenberger2015monetarybenefitfloodwarnings}.
Across many fields, analyses have consistently found that common measures of forecast accuracy do not necessarily correspond directly to measures of the value of forecasts as an input to decision making \cite[e.g.,][]{leitch1991economicForecastEval, murphy1993whatisagoodforecast, cenesizoglu2012returnPredictionEconValue}.

We are aware of only a limited body of work that explicitly attempts to measure the value of infectious disease forecasts through their impact on policy. For example, \cite{ioannidis2022forecastingCOVIDfailed} discuss the possible negative consequences of inaccurate forecasts of infectious disease, but do not attempt to quantify the utility or loss incurred as a result of those forecasts. \cite{bilinski_adaptive_2023} explore ways in which policymaker preferences could inform risk thresholds for predictive models using a framework for measuring the costs and losses associated with taking an action that is similar to methods that have been used in meteorology and elsewhere. \cite{marshall2023predictions} develop a forecast scoring rule that is informally motivated by utility considerations, but the score is not derived from a decision-theoretic set up. Separately, there is a thread of literature that quantifies the link between infectious disease modeling and policy making outside of a forecasting context. As an example, \cite{Probert2016decisionMakingFootMouth} develop measures of the cost of actions designed to control a hypothetical outbreak of foot-and-mouth disease and use this framework to explore policy recommendations from a variety of simulation-based projection models.

In practice, probabilistic infectious disease forecasts have most often been made for observations that emerge from public health surveillance systems and have typically been evaluated with common scoring rules that have implementations available in existing software packages.
For example, seasonal influenza forecasts in the US and dengue forecasts for Peru and Puerto Rico targeted public health surveillance measures of incidence over time and space, and used log-score and mean absolute errors to evaluate forecast skill \citep{mcgowan_collaborative_2019,reich_collaborative_2019,johansson_open_2019}.
Pandemic COVID-19 forecasts of observed cases, hospitalizations and/or deaths in the US and Europe, as reported by municipal, state, or federal surveillance systems, were evaluated using the weighted interval score (WIS, which is an approximation of the continuous ranked probability score, or CRPS), and prediction interval coverage \citep{cramer_evaluation_2022,fox_real-time_2022,sherratt2023predictive}.
Similarly, CRPS was also used to assess probabilistic forecasts of dengue incidence at the district level in Vietnam \citep{colon-gonzalez_probabilistic_2021}.
While some of these scores can be interpreted through the lens of decision theory, and all of the application-specific papers cited above have benefited from direct collaboration with public health agencies, none of them make explicit connections between forecast evaluation and how a forecast was used in practice.

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Mon Jan 29 10:57:25 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
Model & AS & MWIS & IAS centered at 15k & IAS uniform \\ 
  \hline
CU-select & 669 & 133 & 774 & 326 \\ 
  COVIDhub-ensemble & 873 & 159 & 1067 & 438 \\ 
  USC-SI\_kJalpha & 995 & 91 & 1216 & 1097 \\ 
  JHUAPL-Gecko & 1034 & 164 & 1141 & 418 \\ 
  MUNI-ARIMA & 1084 & 169 & 1248 & 440 \\ 
  COVIDhub-trained\_ensemble & 1089 & 169 & 1271 & 823 \\ 
  COVIDhub-baseline & 1175 & 170 & 1317 & 535 \\ 
  JHUAPL-Bucky & 1358 & 102 & 1566 & 1214 \\ 
  JHUAPL-SLPHospEns & 1540 & 129 & 1604 & 1102 \\ 
  UVA-Ensemble & 2469 & 213 & 2635 & 2494 \\ 
   \hline
\end{tabular}
\caption{Comparison of allocation scores (AS), mean weighted interval scores (MWIS), and two varieties of Integrated Allocation Scores (IAS). All metrics are shown for 10 models that made forecasts of hospital admissions for 2022-01-03. Results are sorted by AS. For all metrics, lower scores indicate better accuracy.} 
\label{tab:multi-k-scores}
\end{table}

@@

\section*{Acknowledgements}

We wish to thank the following individuals who contributed valuable comments and feedback on early versions of this work: Matthew Biggerstaff, Rebecca Borchering, Sebastian Funk, Melissa Kerr, and Jeffrey Shaman.

This work has been supported by the National Institutes of General Medical Sciences (R35GM119582) and the U.S. CDC(1U01IP001122). The content is solely the responsibility of the authors and does not necessarily represent the official views of NIGMS, the National Institutes of Health, or CDC.
